Competing Bandits: The Perils of Exploration under Competition

### 2018-09-03 paper/content/model.tex
edits and comments
edits

In some of our experiments, one firm is the ``incumbent" who enters the market before the other (``entrant"). Formally, the incumbent enjoys additional $X$ rounds of the ``warm start". We treat $X$ as an exogenous element of the model, and study the consequences for a fixed $X$.

@@

\end{document}

>>>>

In some of our experiments, one firm is the ``incumbent" who enters the market before the other (``entrant"). Formally, the incumbent enjoys additional $X$ rounds of the ``warm start". We treat $X$ as an exogenous element of the model, and study the consequences for a fixed $X$. 
\swedit{Each firm aims to maximize its market share---the number of agents coming to them.}

@@

\swedit{For any fixed firm, we say that algorithm 1 \emph{weakly
    dominates} algorithm 2 if algorithm 1 never provides a lower
  market share than than 2 against all opposing strategies. An
  algorithm is a weakly dominant strategy for a firm if the algorithm
  weakly dominates all other algorithms.}

\swcomment{please use the above terminology}

\end{document} 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../competing_bandits"
%%% End:
